Fail Faster

### 2025-03-21 paper/paper.tex
blah

We lay a path forward.
First, we show how to use \textit{multi-stage programming}---a classic technique for 
building fast DSLs “without regret”~\cn{}---to eliminate the overhead of 
many common generator abstractions.
Second, we precisely characterize the impact of \rand choice through a natural experiment that preserves 
generator behavior while improving execution speed, demonstrating that the entropy source itself should be treated as a first-class 
concern in generator library design.
Taken together, these insights can be applied to create tomorrow's generator libraries: those that 
combine high-level design with low-level performance.

>>>>

We lay a path forward.
First, we show how to use \textit{multi-stage programming}---a classic technique for 
building fast DSLs “without regret”~\cn{}---to eliminate the overhead of 
many common generator abstractions.
Second, we characterize the impact of \rand choice through a natural experiment 
that isolates the performance contribution of the \rand within a generator, underscoring its role as a first-class design consideration.
Taken together, these insights can be applied to create tomorrow's generator libraries: those that 
combine high-level design with low-level performance.
